---
title: "Bayesian Multi-Species N-Mixture Models for Unmarked Animal Communities"

author:
  - Niamh Mimnagh^1^, Andrew Parnell^1^, Estevão Prado^1^, Rafael de Andrade Moral^2^
  - ^1^Hamilton Institute, Maynooth University, Maynooth, Co. Kildare, Ireland
  - ^2^Department of Mathematics and Statistics, Maynooth University, Maynooth, Co. Kildare, Ireland
output:
  html_notebook: default
---

<style type="text/css">

h1.title {
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  text-align: center;
}

h1, h2, h3 {
  text-align: center;
}
</style>

### Abundance Plots {.tabset}

The following document presents plots of the abundance of each species, per site, per year.

```{r, echo=F}
# Loading data and generating plots
library(rnaturalearth)
library(dplyr)
library(ggplot2)
library(viridis)
library(ggpubr)

load("~/nabbs_models/covariates/sites.RData")
load("~/nabbs_models/covariates/N.RData")
species<-c("Bald_Eagle" , "Canada_Goose","Hammonds_Flycatcher","Red_breasted_Sapsucker","Stellers_Jay","Swainsons_Thrush","Tree_Swallow" ,"Trumpeter_Swan","Varied_Thrush","Wilsons_Snipe" )

Nlist<-vector(mode="list", length=10)
for(s in 1:10){
  Nlist[[s]]<-cbind(N[,s,],sites)
  colnames(Nlist[[s]])<-c(paste(species[s], "2010", sep="_"),paste(species[s], "2011", sep="_"),paste(species[s], "2012", sep="_"), paste(species[s], "2013", sep="_"),paste(species[s], "2014", sep="_"),paste(species[s], "2015", sep="_"), paste(species[s], "2016", sep="_"),paste(species[s], "2017", sep="_"),paste(species[s], "2018", sep="_"), paste(species[s], "2019", sep="_"), "latitude", "longitude")
  
}
names(Nlist)<-species



# Function to produce plot of abundance per species per site
map <- ne_states(country = c('United States of America', 'Canada'), returnclass = 'sf')

x<-vector(mode="list", length=10)
for(s in 1:10){
  colNames<-colnames(Nlist[[s]][,1:10])
  dat<-Nlist[[s]]
  for(i in colNames){
    x[[s]][[i]]<- map %>%
      ggplot(aes(x=longitude, y=latitude))+
      geom_sf(colour = "black", fill = "white", size = 0.2)+
      coord_sf(xlim = c(-168, -131), ylim = c(54, 70), expand = FALSE) +  labs(x = "Longitude", y = "Latitude")+
      geom_point(data=dat, aes_string(color=i), size=6, alpha=0.5)+
      theme(panel.grid.major = element_line(color = gray(.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "cadetblue3"))+
      scale_color_gradient(limits=c(0,max(dat[,1:10])),low="blue", high="red", name="Abundance")+ggtitle(i)+theme(plot.title = element_text(hjust = 0.5))
  }
}
```



#### Bald Eagle
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[1]], ncol=2, nrow=5, legend="bottom")
```

#### Canada Goose
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[2]], ncol=2, nrow=5, legend="bottom")
```

#### Hammond's Flycatcher
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[3]], ncol=2, nrow=5, legend="bottom")
```

#### Red-breasted Sapsucker
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[4]], ncol=2, nrow=5, legend="bottom")
```

#### Steller's Jay
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[5]], ncol=2, nrow=5, legend="bottom")
```

#### Swainson's Thrush
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[6]], ncol=2, nrow=5, legend="bottom")
```

#### Tree Swallow
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[7]], ncol=2, nrow=5, legend="bottom")
```

#### Trumpeter Swan
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[8]], ncol=2, nrow=5, legend="bottom")
```

#### Varied Thrush
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[9]], ncol=2, nrow=5, legend="bottom")
```


#### Wilson's Snipe
```{r, fig.width=16, fig.height=50, echo=F}
ggarrange(plotlist=x[[10]], ncol=2, nrow=5, legend="bottom")
```